Self-test prime dimensional EPR pairs with constant alphabet

### 2019-02-08 Draft/draft.tex
Honghao: expanded Appendix A to add more precise error bound

@@

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{EPR^{(#1)}}
\newcommand{\paulix}{\sigma_x}
\newcommand{\pauliz}{\sigma_z}
\newcommand{\G}{G}
\newcommand{\LS}{LS}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tZ}{\tilde{Z}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}
\newcommand{\dr}[1]{d^{(#1)}}

@@

		\| \Phi( \tilde{A}_x \x \tilde{B}_y \ket{\psi}) -\ket{junk} \x (A_x \x B_y) \ket{\EPR{2}}  \| = O((\alpha+\frac{1}{\alpha}) \sqrt{\epsilon})

@@

\bibliographystyle{alphaurl}
\bibliography{quantum_correlation}
\appendix
%========================================
\section{Proof of \cref{thm:selftest} }
\label{sec:selftest}
%========================================
\begin{proof}
Following the techniques developed in Ref.~\cite{bamps2015}, the first step is to find a sum-of-square decomposition of 
\begin{align}
	\bar{\I}_\alpha = 2\sqrt{\alpha^2+1} \1 - \I_\alpha
	= \frac{2}{\sin(\mu)} \1 - \frac{\cos(\mu)}{\sin(\mu)}(A_1B_1+A_1B_2) -  A_2B_1 + A_2B_2.
\end{align} 
With the following notation
\begin{align*}
	Z_A = A_1 &\quad X_A = A_2\\
	Z_B = \frac{B_1+B_2}{2\cos(\mu)} &\quad X_B = \frac{B_1-B_2}{2\sin(\mu)},
\end{align*}
the two SOS decompositions that we use are
\begin{align}
	\label{eq:sos1}&\bar{\I}_\alpha = \frac{\sin(\mu)\bar{\I}_\alpha^2 + 4\sin(\mu)\cos(\mu)^2(Z_AX_B+X_AZ_B)^2}{4},\\
	\label{eq:sos2}&\bar{\I}_\alpha = \frac{\cos^2(\mu)}{\sin(\mu)}(Z_A-Z_B)^2 + \sin(\mu) (X_A-X_B)^2.
\end{align}
The verification is omitted here.

Suppose the quantum strategy $(\ket{\psi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_{y \in [2]}\}$ achieves that 
$\bra{\psi} \bar{\I}_\alpha \ket{\psi} \leq \epsilon$.
The second step is to establish bounds of the following form
\begin{align}
	\label{eq:zazb} &\|(\tilde{Z}_A-\tilde{Z}_B)\ket{\psi}\| \leq c_1 \sqrt{\epsilon}\\
	&\|(\tilde{X}_A(\1+\tilde{Z}_B)-\tilde{X}_B(\1-\tilde{Z}_A))\ket{\psi}\| \leq c_2 \sqrt{\epsilon}\\
	&\|(\tilde{X}_A-\tilde{X}_B)\ket{\psi}\| \leq c_3 \sqrt{\epsilon}\\
	&\|(\tilde{Z}_A\tilde{X}_A+\tilde{X}_A\tilde{Z}_A)\ket{\psi}\| \leq c_4 \sqrt{\epsilon}.
\end{align}
Now we write $s = \sin(\mu)$, $c = \cos(\mu)$ and define
\begin{align*}
	S_1 &= \frac{\sqrt{s}}{2} \bar{\I}_\alpha, \quad
	S_2 = \sqrt{s}c(\tilde{Z}_A\tilde{X}_B+\tilde{X}_A\tilde{Z}_B),\\
	S_3 &= \frac{c}{\sqrt{s}}(\tilde{Z}_A-\tilde{Z}_B),\quad
	S_4 = \sqrt{s}(\tilde{X}_A-\tilde{X}_B)
\end{align*}
then $\bar{\I}_\alpha = S_1^2 + S_2^2 = S_3^2 + S_4^2$ and $\bra{\psi}\bar{\I}_\alpha \ket{\psi} \leq \epsilon$ implies that 
$\bra{\psi}S^2_i \ket{\psi} \leq \epsilon$ and $\|S_i \ket{\psi} \| \leq \sqrt{\epsilon}$ for $i = 1,2,3,4$.
We can easily check that 
\begin{align*}
	c_1 = \frac{\sqrt{s}}{c}, \quad
	c_2 = \frac{1}{\sqrt{s}} + \frac{1}{c\sqrt{s}}, \quad
	c_3 = \frac{1}{\sqrt{s}}.
\end{align*}
where we use the relation that $\tilde{X}_A(\1+\tilde{Z}_B)-\tilde{X}_B(\1-\tilde{Z}_A) = S_4/s^{1/2} + S_2/(cs^{1/2})$.
To calculate $c_4$, we use the relation
\begin{align}
	\tilde{Z}_A\tilde{X}_A + \tilde{X}_A\tilde{Z}_A = \frac{S_2}{c\sqrt{s}} + \frac{\sqrt{s}\tilde{X}_AS_3}{c} + \frac{\tilde{Z}_AS_4}{\sqrt{s}}
\end{align}
and reach the conclusion that  
\begin{align}
	c_4 = \frac{1+c+s}{c\sqrt{s}}
\end{align}
where we use that fact that $\tilde{Z}_A, \tilde{X}_A$ are unitaries.

With appropriate substitutions, the rest of the proof follows the same derivation as that in Appendix A of Ref.~\cite{bamps2015},
so we omit it here. The dependence of the error term on $\alpha$ comes from the fact that 
\begin{align}
\frac{1}{\cos(\arctan(1/\alpha)) \sin^{1/2}(\arctan(1/\alpha))} = \frac{1}{\alpha}+\frac{3}{4}\alpha - O(\alpha^3).
\end{align}

\end{proof}
%%=====================================
\section{Equations to embed $uxu^{-1} = x^2$}
\label{sec:power2}
%%=====================================
\input{power2_equations}

>>>>

% TikZ
\usepackage{tikz}	
\usetikzlibrary{backgrounds,fit,decorations.pathreplacing}

@@

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{EPR^{(#1)}}
\newcommand{\paulix}{\sigma_x}
\newcommand{\pauliz}{\sigma_z}
\newcommand{\G}{G}
\newcommand{\LS}{LS}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tX}{\tilde{X}}
\newcommand{\tZ}{\tilde{Z}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}
\newcommand{\dr}[1]{d^{(#1)}}

@@

		\| \Phi( \tilde{A}_x \x \tilde{B}_y \ket{\psi}) -\ket{junk} \x (A_x \x B_y) \ket{\EPR{2}}  \| = O((\alpha^2+\frac{1}{\alpha}) \sqrt{\epsilon})

@@

\bibliographystyle{alphaurl}
\bibliography{quantum_correlation}
\appendix
%========================================
\section{Proof of \cref{thm:selftest} }
\label{sec:selftest}
%========================================
This proof follows the same line of argument in Appendix A of Ref.~\cite{bamps2015}.
We first find two sum-of-square decompositions of $2\sqrt{\alpha^2+1} \1 - \I_\alpha$.
The decompositions allow us to determine some key relations between Alice and Bob's observables
and their shared state, which will be used to draw the closeness conclusion.

\begin{proof}
The first step is to find a sum-of-square decomposition of 
the following Bell expression
\begin{align}
	\bar{\I}_\alpha = 2\sqrt{\alpha^2+1} \1 - \I_\alpha
	= \frac{2}{\sin(\mu)} \1 - \frac{\cos(\mu)}{\sin(\mu)}(A_1B_1+A_1B_2) -  A_2B_1 + A_2B_2.
\end{align} 
With the following notation
\begin{align*}
	Z_A = A_1 &\quad X_A = A_2\\
	Z_B = \frac{B_1+B_2}{2\cos(\mu)} &\quad X_B = \frac{B_1-B_2}{2\sin(\mu)},
\end{align*}
the two SOS decompositions that we use are
\begin{align}
	\label{eq:sos1}&\bar{\I}_\alpha = \frac{\sin(\mu)\bar{\I}_\alpha^2 + 4\sin(\mu)\cos(\mu)^2(Z_AX_B+X_AZ_B)^2}{4},\\
	\label{eq:sos2}&\bar{\I}_\alpha = \frac{\cos^2(\mu)}{\sin(\mu)}(Z_A-Z_B)^2 + \sin(\mu) (X_A-X_B)^2.
\end{align}
The verification is omitted here.

Suppose the quantum strategy $(\ket{\psi}, \{\tilde{A}_x\}_{x=1,2}, \{\tilde{B}_{y }\}_{y=1,2}$ achieves that 
$\bra{\psi} \bar{\I}_\alpha \ket{\psi} \leq \epsilon$ where
$\bar{\I}_\alpha$ is expressed with $\tA_x$ and $\tB_y$.
The second step is to establish bounds of the following form
\begin{align}
	\label{eq:zazb} &\|(\tilde{Z}_A-\tilde{Z}_B)\ket{\psi}\| \leq c_1 \sqrt{\epsilon}\\
	\label{eq:xzxz}&\|(\tilde{X}_A(\1+\tilde{Z}_B)-\tilde{X}_B(\1-\tilde{Z}_A))\ket{\psi}\| \leq c_2 \sqrt{\epsilon}\\
	\label{eq:xaxb}&\|(\tilde{X}_A-\tilde{X}_B)\ket{\psi}\| \leq c_3 \sqrt{\epsilon}\\
	\label{eq:anticom} &\|(\tilde{Z}_A\tilde{X}_A+\tilde{X}_A\tilde{Z}_A)\ket{\psi}\| \leq c_4 \sqrt{\epsilon}.
\end{align}
Going back to the sum-of-square decomposition, we write $s = \sin(\mu)$, $c = \cos(\mu)$ and define
\begin{align*}
	S_1 = \frac{\sqrt{s}}{2} \bar{\I}_\alpha, &&
	S_2 = \sqrt{s}c(\tilde{Z}_A\tilde{X}_B+\tilde{X}_A\tilde{Z}_B),\\
	S_3 = \frac{c}{\sqrt{s}}(\tilde{Z}_A-\tilde{Z}_B), &&
	S_4 = \sqrt{s}(\tilde{X}_A-\tilde{X}_B)
\end{align*}
then 
\begin{align}
\bar{\I}_\alpha = S_1^2 + S_2^2 = S_3^2 + S_4^2
\end{align}
 and $\bra{\psi}\bar{\I}_\alpha \ket{\psi} \leq \epsilon$ implies that 
$\bra{\psi}S^2_i \ket{\psi} \leq \epsilon$ and $\|S_i \ket{\psi} \| \leq \sqrt{\epsilon}$ for $i = 1,2,3,4$.
The coefficients $c_1$, $c_2$ and $c_3$ in \cref{eq:zazb,eq:xzxz,eq:xaxb} can be determined from $S_1$,$S_2$ and $S_3$ as
\begin{align*}
	c_1 = \frac{\sqrt{s}}{c}, \quad
	c_2 = \frac{1}{\sqrt{s}} + \frac{1}{c\sqrt{s}}, \quad
	c_3 = \frac{1}{\sqrt{s}}.
\end{align*}
where we use the relation that $\tilde{X}_A(\1+\tilde{Z}_B)-\tilde{X}_B(\1-\tilde{Z}_A) = S_4/s^{1/2} + S_2/(cs^{1/2})$.
To calculate $c_4$, we use the relation
\begin{align}
	\tilde{Z}_A\tilde{X}_A + \tilde{X}_A\tilde{Z}_A = \frac{S_2}{c\sqrt{s}} + \frac{\sqrt{s}\tilde{X}_AS_3}{c} + \frac{\tilde{Z}_AS_4}{\sqrt{s}}
\end{align}
and reach the conclusion that  
\begin{align}
	c_4 = \frac{1+c+s}{c\sqrt{s}}
\end{align}
where we use that fact that $\tilde{Z}_A, \tilde{X}_A$ are unitaries.

Now we introduce the isometries $\Phi_A$ and $\Phi_B$ mentioned in the statement of the theorem.
They are the same as the ones used in Ref.~\cite{bamps2015}.
To construct $\Phi_A$ and $\Phi_B$ we need to regularize $\tZ_B$ and $\tX_B$ to make sure the corresponding operations 
are unitaries in the isometries. We define $\tZ_B^\ast$ to be the operator obtained from $\tZ_B$ by changing all the $0$-eigenvalues
to $1$ and 
\tZ_B' = \tZ_B^\ast |\tZ_B|^{-1}.
In a similar way, we define $\tX_B^\ast$ and $\tX_B'$.
On Alice's side, since $\tZ_A$ and $\tX_A$ are unitaries already,
we define
	\tZ_A' = \tZ_A, && \tX_A' = \tX_A.
The isometries are illustrated in the figure below.
\begin{figure}[H]
\center
        \begin{tikzpicture}[thick]
        %
        % `operator' will only be used by Hadamard (H) gates here.
        % `phase' is used for controlled phase gates (dots).
        % `surround' is used for the background box.
        \tikzstyle{operator} = [draw,fill=white,minimum size=1.5em] 
        \tikzstyle{phase} = [fill,shape=circle,minimum size=5pt,inner sep=0pt]
        \tikzstyle{surround} = [fill=blue!10,thick,draw=black,rounded corners=2mm]
        %
        % Bracket
        \draw[decorate,decoration={brace,mirror},thick] (0,-1) to
    	node[midway,left] (bracket1) {$\ket{\tpsi}$}
    	(0,-2);
        % Qubits
        \node at (0,0) (q1) {$\ket{0}$};
        \node at (0,-1) (q2) {};
        \node at (0,-2) (q3) {};
        \node at (0,-3) (q4) {$\ket{0}$};
        %
        % Column 1
        \node[operator] (op11) at (1,0) {H} edge [-] (q1);
        \node[operator] (op14) at (1,-3) {H} edge [-] (q4);
        %
        % Column 3
        \node[phase] (phase11) at (2,0) {} edge [-] (op11);
	\node[operator] (op22) at (2,-1) {$\tZ_A'$} edge [-] (q2);
	\node[operator] (op23) at (2, -2) {$\tZ_B'$} edge[-] (q3);
        \node[phase] (phase14) at (2,-3) {} edge [-] (op14);
        \draw[-] (phase11) -- (op22);
        \draw[-] (phase14) -- (op23);
        %
        % Column 4
        \node[operator] (op31) at (3,0) {H} edge [-] (phase11);
        \node[operator] (op34) at (3,-3) {H} edge [-] (phase14);
        %
        % Column 5
        \node[phase] (phase21) at (4,0) {} edge [-] (op31);
	\node[operator] (op42) at (4,-1) {$\tX_A'$} edge [-] (op22);
	\node[operator] (op43) at (4, -2) {$\tX_B'$} edge[-] (op23);
        \node[phase] (phase24) at (4,-3) {} edge [-] (op34);
        \draw[-] (phase21) -- (op42);
        \draw[-] (phase24) -- (op43);
        %
        % Column 6
        \node (end2) at (5,-1) {} edge [-] (op42);
        \node (end3) at (5,-2) {} edge [-] (op43);
        %
        % Bracket
        \draw[decorate,decoration={brace},thick] (5,-1) to
    	node[midway,right] (bracket) {$\ket{junk}$}
    	(5,-2);
        %
        % Column 7
        \node (end1) at (6.5,-0.5) {} edge [-] (phase21);
        \node (end4) at (6.5,-2.5) {} edge [-] (phase24);
        % Dashed line
        \draw[loosely dotted] (0,-1.5) -- (5,-1.5);
        % Bracket
        \draw[decorate,decoration={brace},thick,] (6.5,-0.5) to
    	node[midway,right] (bracket2) {$\frac{\ket{00}+\ket{11}}{\sqrt{2}}$}
    	(6.5,-2.5);
        %
        % Background Box
        \begin{pgfonlayer}{background} 
        \node[surround] (background) [fit = (q1) (op14) (bracket1)(bracket2)] {};
        \end{pgfonlayer}
        %
        \end{tikzpicture}
	\caption{The isometries $\Phi_A$ and $\Phi_B$.}
\end{figure}
To bound $e_{xy} := \norm{ (\Phi_A\x\Phi_B) (\tA_x \x \tB_y) \ket{\tpsi} - \ket{junk} \x (A_x\x B_y) \ket{\EPR{2}}}$,
there are some intermediate steps. Since the derivations are the same as in Ref.~\cite{bamps2015}, 
we only record the key relations here.
	&\norm{(\tZ_B' - \tZ_B) \ket{\tpsi}} \leq c_1 \sqrt{\epsilon},\\
	&\norm{(\tZ_B' - \tZ_A') \ket{\tpsi}} \leq 2c_1 \sqrt{\epsilon}, \\
	&\norm{(\tX_B' - \tX_B) \ket{\tpsi}} \leq \frac{c+1}{s^{3/2}} \sqrt{\epsilon} := c_5\sqrt{\epsilon},\\
	&\norm{(\tX_B'\tZ_B'+ \tZ_B'\tX_B')\ket{\tpsi}} \leq [2c_1 + 2c_3 + 2c_5 + (\sqrt{2}+1/c)(2c_1+c_4)]\sqrt{\epsilon}
	:= c_6 \sqrt{\epsilon}.
Then we can calculate that 
	&e_{00} = e_{10} = 2c_6 \sqrt{\epsilon}\\
	&e_{20} = 2(c_4 + c_6) \sqrt{\epsilon}\\
	&e_{01} = e_{02} = e_{11} = e_{12} = [c(c_1)+s(2c_4 + c_5) + 2c_6]\sqrt{\epsilon}\\
	&e_{21} = e_{22} = [2c_4 + c(c_1)+s(2c_4 + c_5) + 2c_6]\sqrt{\epsilon},
so an upper bound of the error is that
	\forall x,y \in \{0,1,2\}, e_{xy} \in O((\frac{1}{cs^{1/2}} + \frac{1}{s^{3/2}})\sqrt{\epsilon}).
The dependence of the error term on $\alpha$ comes from the fact that 
&\frac{1}{\cos(\arctan(1/\alpha)) \sin^{1/2}(\arctan(1/\alpha))} = \frac{1}{\alpha}+\frac{3}{4}\alpha - O(\alpha^3),\\
&\frac{1}{\sin^{3/2}(\arctan(1/\alpha))} = 1 + \frac{3}{4}\alpha^2 - O(\alpha^4).
%%=====================================
\section{Equations to embed $uxu^{-1} = x^2$}
\label{sec:power2}
%%=====================================
\input{power2_equations}
